Supporting information: Copulas and their potential for ecology

### 2019-10-16 SupportingInformation.Rmd
edits to Background section, for clarity

Let $F$ be the bivariate distribution function
of a random vector $(X,Y)$, with margins $F_X$ and $F_Y$ assumed to be 
continuous and strictly monotonic. We show the copula associated with
$(X,Y)$, which exists and is unique by Sklar's theorem, is the distrbution function
of the random variable $(U,V)=(F_X(X),F_Y(Y))$. Let $C$ denote the distribution
function of $(U,V)$, which has uniform margins. By the uniqueness
statement of Sklar's theorem, it suffices to show that $F(x,y)=C(F_X(x),F_Y(y))$
for all $(x,y)$ in the Euclidean plane. But 
$C(F_X(x),F_Y(y)) = P[U \leq F_X(x), V \leq F_Y(y)]
= P[F_X(X) \leq F_X(x), F_Y(Y) \leq F_Y(y)]
= P[X \leq x, Y \leq y]
= F(x,y),$
where the third equality follows from the strict monotonicity assumption. In fact, 
that equality should hold even with non-strict monotonicity, so a stronger 
statement is possible (see below for more on this topic). The continuity assumption 
for $F_X$ and $F_Y$ is necessary, however: without it the random variables 
$U$ and $V$ are not uniformly distributed, so their joint distribution function 
is not even a copula.

>>>>

Let $F$ be the bivariate distribution function
of a random vector $(X,Y)$, with margins $F_X$ and $F_Y$ assumed to be 
continuous and strictly monotonic. We show the copula associated with
$(X,Y)$, which exists and is unique by Sklar's theorem, is, in fact, 
the distribution function
of the random variable $(U,V)=(F_X(X),F_Y(Y))$. Let $C$ denote the distribution
function of $(U,V)$, which has uniform margins. By the uniqueness
statement of Sklar's theorem, it suffices to show that $F(x,y)=C(F_X(x),F_Y(y))$
for all $(x,y)$ in the Euclidean plane. But 
$C(F_X(x),F_Y(y)) = P[U \leq F_X(x), V \leq F_Y(y)]
= P[F_X(X) \leq F_X(x), F_Y(Y) \leq F_Y(y)]
= P[X \leq x, Y \leq y]
= F(x,y),$
where the third equality follows from the strict monotonicity assumption. In fact, 
that equality should hold even with non-strict monotonicity, so a stronger 
statement is possible (see below for more on this topic). The continuity assumption 
for $F_X$ and $F_Y$ is necessary, however: without it the random variables 
$U$ and $V$ are not uniformly distributed, so their joint distribution function 
is not even a copula.
